#Mood Map of the United States
##Beta
####Eric Hullander 2015
"Hello, America, How are ya?""
Using the Twitter API, a random sample of 50,000k twitter tweets are collected daily.  The mood of each tweet is estimated using the AFINN-111.txt dictionary.  You can read about it 
<a href="https://github.com/uwescience/datasci_course_materials/blob/master/assignment1/AFINN-README.txt">here.</a>  The results are then plotted on a map of the US.  This is for entertainment, but there may be some value.  You can see how


```{r setOptions, message=FALSE, echo=FALSE}

require("googleVis")
op <- options(gvis.plot.tag='chart')

DF <- read.csv("tweetscores.csv", colClasses = "character")
DF<-DF[DF$X!="",]
DF$date<-factor(DF$date)
dates<-unique(as.character(DF$date))
#dates

#Google Intensity plot
```
####Mood Date
```{r ComboExample1, results='asis', tidy=FALSE, echo=FALSE}
for (n in 1:length(dates))
  {
  print(dates[n])
  print(weekdays(as.Date(dates[n])))
  df<-subset(DF,date==dates[n])
  Intensity1 <- gvisGeoChart(df, "DMA", "scores", hovervar = "Region",
                           options=list(region="US", displayMode="regions", 
                                        resolution="metros", colors="['#0033CC','#999999','#FFFF00']"))

  plot(Intensity1)
  }
```
####Mood Map
#####Blue=sad
#####Yellow=Happy
```{r ComboExample2, results='asis', tidy=FALSE, echo=FALSE}
for (n in 1:length(dates))
  {
  print(dates[n])
  df<-subset(DF,date==dates[n])
  Intensity2 <- gvisGeoChart(df, "DMA", "count", hovervar = "Region",
                           options=list(region="US", displayMode="regions", 
                                        resolution="metros", colors="['#FFFFFF','#000000']"))

  plot(Intensity2)
  }
```
####Tweet Density
#####Black=More Tweets
#####White=Less Tweets
