#Mood Map of the United States
##Beta
####Eric Hullander 2015
#"Hello, America, How are ya?""
An attempt is made to map the mood of the lower 48.  Using the Twitter API, a random sample of 50,000k twitter tweets are 
collected daily.  The mood of each tweet is estimated using the <a href="https://github.com/uwescience/datasci_course_materials/blob/master/assignment1/AFINN-README.txt">AFINN-111.txt</a> dictionary.  Much of this project builds on a 
course project offered through by Bill Howe of the University of Washington through <a href="https://www.coursera.org/course/datasci">Coursera</a>.
My contribution is in the visualization.  I wanted to see a mood map like a weather map, so I can make better travel plans.  

More to come.  But this week see how Charleston stays kind of blue, and how everything brightens on Saturday.  Maybe it's pride?  Maybe it's meaningless?  

If you're feeling nerdy, <a href="https://github.com/ehullander/Twitterstream">"How I Did It"</a>

####Mood Map
#####Blue=sad
#####Yellow=Happy

```{r setOptions, message=FALSE, echo=FALSE}

require("googleVis")
op <- options(gvis.plot.tag='chart')

DF <- read.csv("tweetscores.csv", colClasses = "character")
DF<-DF[DF$X!="",]
DF$date<-factor(DF$date)
dates<-unique(as.character(DF$date))
#dates

#Google Intensity plot
```
```{r ComboExample1, results='asis', tidy=FALSE, echo=FALSE}
for (n in 1:length(dates))
  {
  print(dates[n])
  print(weekdays(as.Date(dates[n])))
  df<-subset(DF,date==dates[n])
  Intensity1 <- gvisGeoChart(df, "DMA", "scores", hovervar = "Region",
                           options=list(region="US", displayMode="regions", 
                                        resolution="metros", colors="['#0033CC','#999999','#FFFF00']"))

  plot(Intensity1)
  }
```
####Tweet Density
#####Black=More Tweets
#####White=Less Tweets
```{r ComboExample2, results='asis', tidy=FALSE, echo=FALSE}
for (n in 1:length(dates))
  {
  print(dates[n])
  df<-subset(DF,date==dates[n])
  Intensity2 <- gvisGeoChart(df, "DMA", "count", hovervar = "Region",
                           options=list(region="US", displayMode="regions", 
                                        resolution="metros", colors="['#FFFFFF','#000000']"))

  plot(Intensity2)
  }
```

